Using Probabilistic Knockoffs of Binary Variables to Control the False Discovery Rate

### 2015-07-31 masters_paper/paper.tex
Final draft for department

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Variable selection is an essential problem to fitting a regression model. For linear regression, the knockoff filter\cite{2014arXiv1404.5609F} offers a method of exact FDR control. However, the method as originally formulated does not extend to other generalized linear models (GLMs) such as logistic regression. This paper offers an extension of this method for binary features in the context of both GLMs as well as linear regression.

\subsection{Background: the Knockoff Filter}
    Let us consider the usual setting for linear regression, where $n$ observations of a variable of interest $y$ arise from the model
    \[\mathbf{y} = X\beta + \mathbf{z}\]
    where $\mathbf{y}\in\R^n$ are the observed values of $y$, $X \in \R^{n\times p}$ is the matrix of predictor variables, $\beta\in\R^p$ are the unknown coefficients, and $\mathbf z$ is Gaussian noise. It is important to note that a intercept vector $\mathbf 1$ is not included in $X$. For the purpose of this paper, only the case where $2p\leq n$ will be considered, though the methods can be extended to $p\geq n$. I will to refer the $j$th column of $X$ as $X_j$, which is $n$ observations of the random variable $x_j$. The random variable $x_j$ is in turn $j$th entry of the random vector valued variable $\mathbf x$. Let $\beta$ be sparse, implying only a subset of the features $x_j$ have an effect on  $y$. In other words, there is a true model $S\subseteq \{1,\ldots,p\}$ such that $\beta_i\neq0$ if and only if $i\in S$. \par
     In this context, the knockoff filter is designed to choose a model $\hat S$ so as to control the false discovery rate (FDR), or the portion of variables chosen by $\hat S$ which aren't in the true model $S$:
    \[ \textrm{FDR} = \E\left[\frac{\vert{\{j: j\not\in S \; \& \; j\in\hat S\}}\vert}{\max\{\vert{\hat S}\vert,1\}} \right] \]
    In other words, FDR is the portion of features which are thought to have an effect on $y$ but actually have no effect. FDR is controlled at level $q$ if FDR is less than or equal to $q$ irrespective of the coefficients $\beta$. \par

@@

    for some vector $\mathbf{s}\in \R^p$ such that, writing $\diag{G}$ as the vector made from the main diagonal of $G$, $\diag{G} - \mathbf s$ has small magnitude. Since $\tilde X_j$ and $X_j$ have relatively low correlation, as long as $X_j$ is created independently of $\mathbf y$, $\tilde X_j$ will have lower correlation with $\mathbf y$ than $X_j$. In the case where $X_j$ is a null predictor of $\mathbf y$, $\tilde X_j$ will thus also be a null predictor of $\mathbf y$. How these knockoffs are actually generated will be described shortly.\par

@@

            $W_j$ is positive when $Z_j$ entered the path first and negative when $\tilde X_j$ entered the path first. Large, positive values for $W_j$ will indicate that $X_j$ is a strong predictor, since $X_j$ entered the path early and before $\tilde X_j$. Thus, we will make a selection $\hat S=\{j:W_j\geq T\}$ for some threshold $T$. When $j\not\in S$, $X_j$ and $\tilde X_j$ are both equally likely to enter the path first, so $W_j$ is equally as likely to be positive as negative for $j\in S$. Thus, 

@@

            \[\vert \{j:W_j\leq -T \; \& \; j\not\in S\}\vert \leq \vert\{j:W_j\leq -T\}\vert\]

@@

            \[FDR \approx \E\left[\frac{\vert\{j:W_j\leq -T\}\vert}{\max\{\vert\{j:W_j\geq T\}\vert,1\}}\right]\] 

@@

\subsection{Original Knockoff Features}
    The original formulation of the method offers two similar methods of constructing knockoffs. Both of these will, by construction, have exactly the property that
    \[ \tilde X^T\tilde X=G \textrm{ and } \tilde X^T X = G - \diag{\mathbf s}.\]
    For both methods, the first step is to normalize the matrix $X$ such that $X_j^TX_j=1$ for all $j$. The Gram matrix of $X_{aug}$ is
    \[ G_{aug}:= [X\; \tilde X]^T[X\; \tilde X] = \left[ \begin{array}{cc} G & G - \diag{\mathbf s} \\ G - \diag{\mathbf s} & G \end{array}\right] \]
    $A$, the Schur complement of $G$ in $G_{aug}$ can be calculated as 
    \[ A = 2\,\diag{\mathbf s} - \diag{\mathbf s}G^{-1}\diag{\mathbf s} \]
    For $G_{aug}$ to exist, $G_{aug}$ must be positive semi-definite, which happens if and only if $A$ is positive semi-definite, which happens in turn if and only if 
    \[ \diag{\mathbf s} \succeq 0  \; \textrm{ and } \; 2G - \diag{\mathbf s} \succeq 0 \]
    Given this is true, $A$ can be factored as $A=C^TC$. Combining this with a satisfactory $\mathbf s$ and an orthonormal matrix $\tilde U\in\R^{n\times p}$ such that $\tilde U^T X = 0$, a $\tilde X$ fulfilling the desired properties can be calculated as 
    \[ \tilde X = X(I-G^{-1}\,\diag{\mathbf s}) + \tilde UC\]
    As mentioned above, $\mathbf s$ should be chosen so as to make $\diag{G}-\mathbf s$ small. Since each $X_j$ has been normalized, this means that $\diag{G}=\mathbf 1$, so $\mathbf 1 - \mathbf s$ should be minimized in accordance with the restrictions on $\mathbf s$. The two methods differ in how $\mathbf s$ is chosen:
    \begin{itemize}
        \item \textit{Equi-correlated knockoffs}: Each original features is set to have the same correlation with its knockoff by setting $\mathbf s = 2\min\{\lambda_{min}(G),1\}\mathbf 1$. For all simulations in this paper, this was the method used.
        \item \textit{SDP knockoffs}: The $\mathbf s$ which minimizes the average correlation between knockoff and original features can be found via a semi-definite programing problem:
            \begin{center}
                \begin{tabular}{r l}
                    minimize & $\|\mathbf1-\mathbf s\|_1$ \\
                    subject to & $ 0 \preceq \diag{\mathbf s} \preceq 2G $
                \end{tabular} 
            \end{center}
            This method is significantly more computationally intensive. 
    \end{itemize}

\subsection{Binary Knockoffs}
    Though the ``original" knockoff method, described above, achieves the exact desired correlation properties, the individual values in the vector $X_j$ will have little relation to the individual values in $X_j$. In particular, these values will often have very different empirical distributions. This effect is particularly noticeable when the random variable $x_j$ is discrete but $\tilde X_j$ does not even consist of the same set of values. The end result is that for variable selection for other generalized linear models, which do not have the same sufficient statistics which knockoffs are designed to replicate, the original knockoffs will fail to control FDR. \par
    Thus, this paper offers a new method of generating knockoffs for binary data which should offer superior performance with other GLMs. In this new method, the matrix of knockoff features $\tilde X$ will also be binary, generated randomly so as to hit the new correlation condition
    \[ \E[\mathbf{\tilde x}^T\mathbf{\tilde x}]=\Sigma \; \textrm{ and } \; \E[\mathbf{\tilde x}^T \mathbf x \st \mathbf x] = \Sigma - \diag{\mathbf s}\]
    Where $\Sigma$ is the covariance matrix of $X$. This is essentially a relaxation of the original correlation condition, requiring the desired covariance to only hold in expectation. For large values of $n$, the observed covariance will converge to its expectation, making this distinction minor.

@@

    The $Z_j$ and $\tilde Z_j$ are then, once again, the largest $\lambda$ such that the given original or knockoff feature has a positive coefficient, and then $W_j$ is constructed exactly as before. The problem with this is that if the given GLM doesn't have the same sufficient statistics as linear regression, there is no theoretical guarantee that the knockoff filter will control FDR. This is since, for null $X_j$, there is no theory to guarantee the $Z_j$ and $\tilde Z_j$ are exchangeable, and thus $W_j$ is not guaranteed to be symmetrically distributed around $0$. \par
    \begin{figure}[h]
        \begin{center}
        \includegraphics[width=14cm]{images/entryrate_original_logit}
    \end{center}
    \caption{\linespread{1}\selectfont{} The mean cumulative portion of $W$ statistic which are positive by absolute rank of the value. The mean is over 1000 simulations. On the left side, the features are drawn from a random standard normal distribution. On the right side, they are drawn as Bernoulli with probability $.25$ of being 1. The top has 50 null features, while the bottom has 10 features in the true model, and 40 null features.}
    \end{figure}

@@

    To evaluate whether this made a difference in practice, I tested the method using original style knockoffs in logistic regression. The results can be seen in figure 1, which shows cumulatively, starting with the largest absolute value, what portion of the $W_j$ are positive. For the method to work, for the null predictors, this should be a consistent $50\%$, indicative of the desired symmetric distribution. This is particularly important for high values, which play the largest roll in selecting a threshold. In the top left corner, under the ``global null", where all features are null and normally distributed, we almost achieve this. There is just a small, but consistent, deviation from $50\%$. However, in the top right, when the predictors are binary but still all null, the originals enter first far more often, which will result in the FDR being too high. \par
    \begin{figure}[h]
        \begin{center}
            \includegraphics[width=14cm]{images/normalQQ}
            \caption{\linespread{1}\selectfont{}Normal Q-Q of original variables and knockoffs for simulation with $4$ variables and 1,000 observations}
        \end{center}
    \end{figure}

    This gets much worse when some true predictors are included, as shown in the bottom row of the figure. For both normal and binary predictors, the originals come in first far more often in the beginning. This will completely ruin FDR control, since the portion of null predictors will be assumed far lower than it actually is. It is worth noting that the particular shape of the curve in the diagram, with the plateau for the null predictors through 10, is partially an artifact of there being 10 true signals. The mean through the first ten is the mean for null predictors that came in first out of both null and true predictors; since the largest ten $W_j$ will tend to be true predictors, the average over the null predictors represent the few extreme $W_j$ which managed to beat out some number of true predictors.  \par
    Upon examination, the issue seems to be that the original style knockoff features have a very different empirical distribution than the features they are imitating. This is obviously true with the binary features, but even with the normal features, the distributions differ substantially. In figure 2, the distribution of four features and their original style knockoff are plotted against a normal distribution in Q-Q plots. As you can see, the distributions differ substantially. This is suggestive of a solution; if the knockoff variables match the marginal distribution of the original features better, the result may be more suitable for FDR control in GLMs. \par
    \FloatBarrier

\section{Random Binary Knockoffs}
Coming up with knockoffs which would match the original features' marginal distributions better for arbitrary $X$ is daunting problem. Limiting ourselves to binary data, which is common in real world applications, presents a far more manageable case. However, solving for a binary $\tilde X$ which matches the correlation condition exactly or closely is an integer programing problem, which are generally NP-hard. Thus, instead, this section will develop methods of generating $\tilde X$ randomly such that the correlation condition holds in expectation. Mainly, $\tilde X\st X$ should be a random binary matrix such that
        \[ \E(X^T \tilde X \st X) = X^TX - \diag{s} \quad \& \quad \E(\tilde X^T \tilde X \st X) = X^TX\]

\subsection{Random Binary Vector Variables}
We can imagine each row of $X$ being an observation of a random binary vector variable $\mathbf x$. The full class of random binary vector variables on $\{0,1\}^p$ can be specified as multinomial on the $2^p$ elements of the set. However, it is generally impractical to specify or estimate all $2^p-1$ necessary parameters, so it is useful to pick a method to match the first two moments, as is desirable for knockoffs. These are the mean vector $\E(\mathbf x)=\mathbf{m}\in[0,1]^p$ and the cross-moment matrix $\E(\mathbf x\mathbf x^T)=M\in[0,1]^{p\times p}$. Obviously, $m_i = \p(x_i=1)$, $M_{ij} = \p(x_i=x_j=1)$, and $\mathbf m=\diag{M}$. For an arbitrary symmetric $M$ to be a valid cross-moment matrix for some random binary vector variable, $M-mm^T\succeq0$, and
    \[ \max\{0,m_i+m_j -1\} \leq M_{ij} \leq \min\{m_i,m_j\}\]
    for all $i\neq j$.\cite{2011arXiv1111.0576S}

\subsection{Relaxed Correlation Condition}
As before with the original knockoffs, the first step of generating knockoffs is to decide on the target correlation structure for $X_{aug}$. For binary knockoffs, this is done by selecting the target covariance matrix $\Sigma_{aug}$. This is extremely similar, though not identical, to the method with the original knockoffs, where $X_{aug}^TX_{aug}$ after normalization was targeted. However, much the same method as before can be used. Let the vector of empirical means of the columns of $X$ be $\mathbf m = \frac{1}{n}X^T\mathbf 1$ and the empirical covariance matrix of $X$ be $\Sigma = \frac{1}{n}X^TX - \mathbf{m}\mathbf{m}^T$. Much as before with the original knockoffs, both the equi-correlated and SDP method can be used to select  $\mathbf s$  such that $\diag{\Sigma}-\mathbf s$ has small magnitude and 
        \[ \Sigma_{aug} = \left[\begin{array}{cc}  \Sigma & \Sigma - \diag{\mathbf s }\\ \Sigma - \diag{\mathbf s} & \Sigma \end{array}\right] \succeq 0 \]
    While with the original knockoffs, the result was small values for $X_i^T\tilde X_i$, now the result is low covariance between $X_i$ and $\tilde X_i$.\par
    Additionally though, the moment condition must hold for $\Sigma_{aug}$ to correspond to a proper random binary vector. If 
    \[\mathbf m_{aug} = \E\left(\mathbf x_{aug}\right) = \left[\begin{array}{c}\mathbf m \\ \mathbf m \end{array}\right] \]
    then the desired cross-moment matrix of the joint distribution is 
        \[ M_{aug} = \Sigma_{aug} + \mathbf m_{aug}\mathbf m_{aug}^T\]
        As mentioned above, for this cross-moment matrix to correspond to an actual random binary vector, it must be the case  
        \[\max\{0,(m_{aug})_i + ( m_{aug})_j -1\} \leq (\Sigma_{aug})_{ij} +  (m_{aug})_i  (m_{aug})_j \leq \min\{( m_{aug})_i, ( m_{aug})_j\} \]
    However, since $\Sigma$ and $\mathbf m$ are from an actual random binary vector, the entries of $\Sigma$ satisfy this property by default. Only off diagonal entries which have had $\mathbf s$ subtracted from them could possibly violate this condition. Furthermore, for these entries, the goal is to make $(\Sigma_{aug})_{ij}$ as close to $0$ as possible. Since the condition is always satisfied in a neighborhood of $(M_{aug})_{ij} = (m_{aug})_j(m_{aug})_i$, this implies that this method should normally be satisfied. This is the principle advantage of minimizing the $\textrm{cov}(x_i,\tilde x_i)$ rather than $\E[x_i\tilde x_i]$. For the SDP method though, the restriction can be built directly into the optimization problem. If $\sigma = \diag{\Sigma}^{\frac{1}{2}}$ is the vector of standard deviations, the updated problem is
            \begin{center}
                \begin{tabular}{r l}
                    minimize & $\|\mathbf 1-\diag{\sigma}^{-1}\mathbf s\|_1$ \\
                    subject to & $ 0 \preceq \diag{\mathbf s} \preceq 2\Sigma $ \\
                               & $ \max\{2m_i -1,0\} \leq \Sigma_{ii}-s_i + m_i^2 \leq m_i  \quad \forall i$
                \end{tabular} 
            \end{center} 
            the factor of $\diag{\sigma}^{-1}$ in the objective is to account for the $x_i$ not being normalized, as was the case with the original knockoffs. \par
            Given the $\Sigma_{aug}$ and corresponding $M_{aug}$, all that is needed is some process to generate $\tilde X$ that replicates the desired empirical cross moments.

\subsection{Fitting via Quadratic Programing}
        The simplest way to do this is based on a probability matrix $P\in (0,1)^{n\times p}$, where each $X_{ij}$ is drawn independently as $X_{ij}\sim\textrm{Bernoulli}(P_{ij})$. Such a $P$ should satisfy 
            \begin{center}
                \begin{tabular}{r l}
                    minimize     & $\|X^TP-(M-\diag{s})\|_{fro}^2 + \sum_{i\neq j}(P_i^T P_j - M_{ij})^2 $\\
                    subject to   & $ \mathbf 1^T P = \mathbf m $ \\
                                 & $0 \leq P \leq 1$
                \end{tabular} 
            \end{center}
            so that the cross-moments are as close as possible to $M_{aug}$. The first part of the objective corresponds to the deviation of $\E[X^T\tilde X]$ from $M-\diag{s}$ and the second part to the deviation of $\E[\tilde X^T \tilde X]$ from $M$ excluding the diagonal values which are matched by $ \mathbf 1^T P = \mathbf m $. This problem can be stated as a quadratic program via the introduction of slack variables:
            \begin{center}
                \begin{tabular}{r l}
                    minimize     & $\|W\|_{fro}^2 + \|V\|_{fro}^2 $ \\
                    subject to   & $ -W \leq X^TP-(M-\diag{s})\leq W $ \\
                                 & $ -V_{ij} \leq P_i^T P_j - M_{ij} \leq V_{ij} \quad \forall i\neq j$ \\
                                 & $ \mathbf 1^T P = \mathbf m $ \\
                                 & $0 \leq P \leq 1$
                \end{tabular} 
            \end{center}

@@

        \[ J\left( \mathbf a_i\right) = \sum_{\xi_{-i} \in \{0,1\}^{i-1}} \frac{1}{c}L\left(\mathbf \xi_{-i}^TA_{-i}\xi_{-i}\right) L'\left(\mathbf{a}_i^T\left[\begin{array}{c} \mathbf \xi_{-i} \\ 1 \end{array}\right]\right)\left[\begin{array}{c} \xi_{-i} \\ 1 \end{array}\right]\left[\begin{array}{cc} \xi_{-i}^T & 1 \end{array}\right] \]

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Variable selection is an essential problem to fitting a regression model. For linear regression, the knockoff filter \cite{2014arXiv1404.5609F} offers a method of exact FDR control. However, the method as originally formulated does not extend to other generalized linear models (GLMs) such as logistic regression. This paper offers an extension of this method for binary features in the context of both GLMs as well as linear regression.

\subsection{Background: the Knockoff Filter}
    Let us consider the usual setting for linear regression, where $n$ observations of a variable of interest $y$ arise from the model
    \[\mathbf{y} = X\beta + \mathbf{z}\]
    where $\mathbf{y}\in\R^n$ are the observed values of $y$, $X \in \R^{n\times p}$ is the matrix of predictor variables, $\beta\in\R^p$ are the unknown coefficients, and $\mathbf z$ is Gaussian noise. It is important to note that a intercept vector $\mathbf 1$ is not included in $X$. For the purpose of this paper, only the case where $2p\leq n$ will be considered, though the methods can be extended to $p\geq n$. I will to refer the $j$th column of $X$ as $X_j$, which is $n$ observations of the random variable $x_j$. The random variable $x_j$ is in turn the $j$th entry of the random vector valued variable $\mathbf x$. Let $\beta$ be sparse, implying only a subset of the features $x_j$ have an effect on  $y$. In other words, there is a true model $S\subseteq \{1,\ldots,p\}$ such that $\beta_i\neq0$ if and only if $i\in S$. \par
     In this context, the knockoff filter is designed to choose a model $\hat S$ so as to control the false discovery rate (FDR), or the portion of variables chosen by $\hat S$ which aren't in the true model $S$:
    \[ \textrm{FDR} = \E\left[\frac{\vert{\{j: j\not\in S \; \& \; j\in\hat S\}}\vert}{\max\{\vert{\hat S}\vert,1\}} \right] \]
    In other words, FDR is the portion of features which are thought to have an effect on $y$ but actually have no effect. FDR is controlled at level $q$ if FDR is less than or equal to $q$ irrespective of the coefficients $\beta$. \par

@@

    for some vector $\mathbf{s}\in \R^p$ such that, writing $\diag{G}$ as the vector made from the main diagonal of $G$, $\diag{G} - \mathbf s$ has small magnitude. Since $\tilde X_j$ and $X_j$ have relatively low correlation, as long as $\tilde X_j$ is created independently of $\mathbf y$, $\tilde X_j$ will have lower correlation with $\mathbf y$ than $X_j$ if $X_j$ is a true predictor. In the case where $X_j$ is a null predictor of $\mathbf y$, $\tilde X_j$ will thus also be a null predictor of $\mathbf y$. How these knockoffs are actually generated will be described shortly.\par

@@

            $W_j$ is positive when $X_j$ enters the path first and negative when $\tilde X_j$ enters the path first. Large, positive values for $W_j$ will indicate that $X_j$ is a strong predictor, since $X_j$ enters the path early and before $\tilde X_j$. Thus, we will make a selection $\hat S=\{j:W_j\geq T\}$ for some threshold $T$. When $j\not\in S$, $X_j$ and $\tilde X_j$ are both equally likely to enter the path first, so $W_j$ is equally as likely to be positive as negative for $j\in S$. Thus, 

@@

            \[\vert \{j:W_j\leq -T \; \& \; j\not\in S\}\vert \leq \vert\{j:W_j\leq -T\}\vert.\]

@@

            \[FDR \approx \E\left[\frac{\vert\{j:W_j\leq -T\}\vert}{\max\{\vert\{j:W_j\geq T\}\vert,1\}}\right].\] 

@@

\subsection{Original Knockoff Features}
    The original formulation of the method offers two similar methods of constructing knockoffs. Both of these will, by construction, have exactly the property that
    \[ \tilde X^T\tilde X=G \textrm{ and } \tilde X^T X = G - \diag{\mathbf s}.\]
    For both methods, the first step is to normalize the matrix $X$ such that $X_j^TX_j=1$ for all $j$. The Gram matrix of $X_{aug}$ is
    \[ G_{aug}:= [X\; \tilde X]^T[X\; \tilde X] = \left[ \begin{array}{cc} G & G - \diag{\mathbf s} \\ G - \diag{\mathbf s} & G \end{array}\right]. \]
    $A$, the Schur complement of $G$ in $G_{aug}$, can be calculated as 
    \[ A = 2\,\diag{\mathbf s} - \diag{\mathbf s}G^{-1}\diag{\mathbf s}. \]
    For $G_{aug}$ to exist, $G_{aug}$ must be positive semi-definite, which happens if and only if $A$ is positive semi-definite, which happens in turn if and only if 
    \[ \diag{\mathbf s} \succeq 0  \; \textrm{ and } \; 2G - \diag{\mathbf s} \succeq 0. \]
    Given this is true, $A$ can be factored as $A=C^TC$. Combining this with a satisfactory $\mathbf s$ and an orthonormal matrix $\tilde U\in\R^{n\times p}$ such that $\tilde U^T X = 0$, a $\tilde X$ fulfilling the desired properties can be calculated as 
    \[ \tilde X = X(I-G^{-1}\,\diag{\mathbf s}) + \tilde UC.\]
    As mentioned above, $\mathbf s$ should be chosen so as to make $\diag{G}-\mathbf s$ small. Since each $X_j$ has been normalized, this means that $\diag{G}=\mathbf 1$, so $\mathbf 1 - \mathbf s$ should be minimized in accordance with the restrictions on $\mathbf s$. The two methods differ in how $\mathbf s$ is chosen:
    \begin{itemize}
        \item \textit{Equi-correlated knockoffs}: Each original features is set to have the same correlation with its knockoff by setting $\mathbf s = 2\min\{\lambda_{min}(G),1\}\mathbf 1$. For all simulations in this paper, this was the method used.
        \item \textit{SDP knockoffs}: The $\mathbf s$ which minimizes the average correlation between knockoff and original features can be found via a semi-definite programing problem:
            \begin{center}
                \begin{tabular}{r l}
                    minimize & $\|\mathbf1-\mathbf s\|_1$ \\
                    subject to & $ 0 \preceq \diag{\mathbf s} \preceq 2G $
                \end{tabular} 
            \end{center}
            This method is significantly more computationally intensive. 
    \end{itemize}

\subsection{Binary Knockoffs}
    Though the ``original" knockoff method, described above, achieves the exact desired correlation properties, the individual values in the vector $X_j$ will have little relation to the individual values in $X_j$. In particular, these values will often have very different empirical distributions. This effect is particularly noticeable when the random variable $x_j$ is discrete but $\tilde X_j$ does not even consist of the same set of values. The end result is that for variable selection for other generalized linear models, which do not have the same sufficient statistics which knockoffs are designed to replicate, the original knockoffs will fail to control FDR. \par
    Thus, this paper offers a new method of generating knockoffs for binary data which should offer superior performance with other GLMs. In this new method, the matrix of knockoff features $\tilde X$ will also be binary, generated randomly so as to hit the new correlation condition
    \[ \E[\mathbf{\tilde x}^T\mathbf{\tilde x}]=\Sigma \; \textrm{ and } \; \E[\mathbf{\tilde x}^T \mathbf x \st \mathbf x] = \Sigma - \diag{\mathbf s}\]
    where $\Sigma$ is the covariance matrix of $X$. This is essentially a relaxation of the original correlation condition, requiring the desired covariance to only hold in expectation. For large values of $n$, the observed covariance will converge to its expectation, making this distinction minor.

@@

    The $Z_j$ and $\tilde Z_j$ are then, once again, the largest $\lambda$ such that the given original or knockoff feature has a positive coefficient, and then $W_j$ is constructed exactly as before. The is that if the given GLM doesn't have the same sufficient statistics as linear regression, there is no theoretical guarantee that the knockoff filter will control FDR. This is since, for null $X_j$, there is no guarantee the $Z_j$ and $\tilde Z_j$ are exchangeable, and thus $W_j$ is not guaranteed to be symmetrically distributed around $0$ for null features $X_j$. \par
    \begin{figure}[h]
        \begin{center}
        \includegraphics[width=14cm]{images/entryrate_original_logit}
    \end{center}
    \caption{\linespread{1}\selectfont{} The mean cumulative portion of $W$ statistic which are positive by absolute rank of the value. The mean is over 1000 simulations. On the left side, the features are drawn from a random standard normal distribution. On the right side, they are drawn as Bernoulli with probability $.25$ of being 1. The top has 50 null features, while the bottom has 10 features in the true model, and 40 null features.}
    \end{figure}

@@

    To evaluate whether this made a difference in practice, I tested the method using original style knockoffs in logistic regression. The results can be seen in figure 1, which shows cumulatively, starting with the largest absolute value, what portion of the $W_j$ are positive. For the method to work, for the null predictors, this should be a consistent $50\%$, indicative of the desired symmetric distribution. This is particularly important for high values of $|W_j|$, which play the largest roll in selecting a threshold. In the top left corner, under the ``global null", where all features are null and normally distributed, we almost achieve this. There is just a small, but consistent, deviation from $50\%$. However, in the top right, when the predictors are binary but still all null, the originals enter first far more often, which will result in the FDR being too high. \par
    \begin{figure}[h]
        \begin{center}
            \includegraphics[width=14cm]{images/normalQQ}
            \caption{\linespread{1}\selectfont{}Normal Q-Q of original variables and knockoffs for simulation with $4$ variables and 1,000 observations}
        \end{center}
    \end{figure}

    This gets much worse when some true predictors are included in the model, as shown in the bottom row of the figure. For both normal and binary predictors, the originals come in first far more often in the beginning. This will completely ruin FDR control, since the portion of null predictors will be assumed far lower than it actually is. It is worth noting that the particular shape of the curve in the diagram, with the plateau for the null predictors through 10, is partially an artifact of there being 10 true signals. The mean through the first ten is the mean for null predictors that came in first out of both null and true predictors; since the largest ten $W_j$ will tend to be true predictors, the average over the null predictors represent the few extreme $W_j$ which managed to beat out some number of true predictors.  \par
    Upon examination, one issue seems to be that the original style knockoff features have a very different empirical distribution than the features they are imitating. This is obviously true with the binary features, but even with the normal features, the distributions differ substantially. In figure 2, the distribution of four features and their original style knockoff are plotted against a normal distribution in Q-Q plots. As you can see, the distributions differ substantially. This is suggestive of a solution; if the knockoff variables match the marginal distribution of the original features better, the result may be more suitable for FDR control in GLMs. \par
    \FloatBarrier

\section{Random Binary Knockoffs}
Coming up with knockoffs which would match the original features' marginal distributions better for arbitrary $X$ is daunting problem. Limiting ourselves to binary data, which is common in real world applications, presents a far more manageable case. However, solving for a binary $\tilde X$ which matches the correlation condition exactly or closely is an integer programing problem, which are generally NP-hard. Thus, instead, this section will develop methods of generating $\tilde X$ randomly such that the correlation condition holds in expectation. Mainly, $\tilde X\st X$ should be a random binary matrix such that
    \[ \E[X^T \tilde X \st X] = X^TX - \diag{\mathbf s} \quad \& \quad \E[\tilde X^T \tilde X \st X] = X^TX.\]

\subsection{Random Binary Vector Variables}
We can imagine each row of $X$ being an observation of a random binary vector variable $\mathbf x$. The full class of random binary vector variables on $\{0,1\}^p$ can be specified as multinomial on the $2^p$ elements of the set. However, it is generally impractical to specify or estimate all $2^p-1$ necessary parameters, so it is useful to pick a method to match the first two moments, as is desirable for knockoffs. These are the mean vector $\E(\mathbf x)=\mathbf{m}\in[0,1]^p$ and the cross-moment matrix $\E(\mathbf x\mathbf x^T)=M\in[0,1]^{p\times p}$. Obviously, $m_i = \p(x_i=1)$, $M_{ij} = \p(x_i=x_j=1)$, and $\mathbf m=\diag{M}$. For an arbitrary symmetric $M$ to be a valid cross-moment matrix for some random binary vector variable, the necessary and sufficient conditions are that $M-mm^T\succeq0$ and
    \[ \max\{0,m_i+m_j -1\} \leq M_{ij} \leq \min\{m_i,m_j\}\]
    for all $i\neq j$ \cite{2011arXiv1111.0576S}.

\subsection{Relaxed Correlation Condition}
As before with the original knockoffs, the first step of generating knockoffs is to decide on the target correlation structure for $X_{aug}$. For binary knockoffs, this is done by selecting the target covariance matrix $\Sigma_{aug}$. This is extremely similar, though not identical, to the method with the original knockoffs, where $X_{aug}^TX_{aug}$ after normalization was targeted. However, much the same method as before can be used. Let the vector of empirical means of the columns of $X$ be $\mathbf m = \frac{1}{n}X^T\mathbf 1$ and the empirical covariance matrix of $X$ be $\Sigma = \frac{1}{n}X^TX - \mathbf{m}\mathbf{m}^T$. Much as before with the original knockoffs, both the equi-correlated and SDP method can be used to select  $\mathbf s$  such that $\diag{\Sigma}-\mathbf s$ has small magnitude and 
        \[ \Sigma_{aug} = \left[\begin{array}{cc}  \Sigma & \Sigma - \diag{\mathbf s }\\ \Sigma - \diag{\mathbf s} & \Sigma \end{array}\right] \succeq 0. \]
    While with the original knockoffs, the result was small values for $X_i^T\tilde X_i$, now the result is low covariance between $X_i$ and $\tilde X_i$.\par
    Additionally though, the moment condition must hold for $\Sigma_{aug}$ to correspond to a proper random binary vector. If 
    \[\mathbf m_{aug} = \E\left(\mathbf x_{aug}\right) = \left[\begin{array}{c}\mathbf m \\ \mathbf m \end{array}\right] \]
    then the desired cross-moment matrix of the joint distribution is 
        \[ M_{aug} = \Sigma_{aug} + \mathbf m_{aug}\mathbf m_{aug}^T.\]
        As mentioned above, for this cross-moment matrix to correspond to an actual random binary vector, it must be the case  
        \[\max\{0,(m_{aug})_i + ( m_{aug})_j -1\} \leq (\Sigma_{aug})_{ij} +  (m_{aug})_i  (m_{aug})_j \leq \min\{( m_{aug})_i, ( m_{aug})_j\}. \]
    However, since $\Sigma$ and $\mathbf m$ are from an actual random binary vector, the entries of $\Sigma$ satisfy this property by default. Only off diagonal entries which have had $\mathbf s$ subtracted from them could possibly violate this condition. Furthermore, for these entries, the goal is to make $(\Sigma_{aug})_{ij}$ as close to $0$ as possible. Since the condition is always satisfied in a neighborhood of $(M_{aug})_{ij} = (m_{aug})_j(m_{aug})_i$, this implies that this method should normally be satisfied. This is the principle advantage of minimizing the $\textrm{cov}(x_i,\tilde x_i)$ rather than $\E[x_i\tilde x_i]$. For the SDP method though, the restriction can be built directly into the optimization problem. If $\sigma = \diag{\Sigma}^{\frac{1}{2}}$ is the vector of standard deviations, the updated problem is
            \begin{center}
                \begin{tabular}{r l}
                    minimize & $\|\mathbf 1-\diag{\sigma}^{-1}\mathbf s\|_1$ \\
                    subject to & $ 0 \preceq \diag{\mathbf s} \preceq 2\Sigma $ \\
                               & $ \max\{2m_i -1,0\} \leq \Sigma_{ii}-s_i + m_i^2 \leq m_i  \quad \forall i$
                \end{tabular} 
            \end{center} 
            the factor of $\diag{\sigma}^{-1}$ in the objective is to account for the $x_i$ not being normalized, as was the case with the original knockoffs. \par
            Given the $\Sigma_{aug}$ and corresponding $M_{aug}$, all that is needed is some process to generate $\tilde X$ that replicates the desired empirical cross moments.

\subsection{Fitting via Quadratic Programing}
        The simplest way to do this is based on a probability matrix $P\in (0,1)^{n\times p}$, where each $X_{ij}$ is drawn independently as $X_{ij}\sim\textrm{Bernoulli}(P_{ij})$. Such a $P$ should satisfy 
            \begin{center}
                \begin{tabular}{r l}
                    minimize     & $\|X^TP-(M-\diag{\mathbf{s}})\|_{fro}^2 + \sum_{i\neq j}(P_i^T P_j - M_{ij})^2 $\\
                    subject to   & $ \mathbf 1^T P = \mathbf m $ \\
                                 & $0 \leq P \leq 1$
                \end{tabular} 
            \end{center}
            so that the cross-moments are as close as possible to $M_{aug}$. The first part of the objective corresponds to the deviation of $\E[X^T\tilde X]$ from $M-\diag{\mathbf{s}}$ and the second part to the deviation of $\E[\tilde X^T \tilde X]$ from $M$ excluding the diagonal values which are matched by $ \mathbf 1^T P = \mathbf m $. This problem can be stated as a quadratic program via the introduction of slack variables:
            \begin{center}
                \begin{tabular}{r l}
                    minimize     & $\|W\|_{fro}^2 + \|V\|_{fro}^2 $ \\
                    subject to   & $ -W \leq X^TP-(M-\diag{\mathbf{s}})\leq W $ \\
                                 & $ -V_{ij} \leq P_i^T P_j - M_{ij} \leq V_{ij} \quad \forall i\neq j$ \\
                                 & $ \mathbf 1^T P = \mathbf m $ \\
                                 & $0 \leq P \leq 1$
                \end{tabular} 
            \end{center}

@@

        \[ J\left( \mathbf a_i\right) = \sum_{\xi_{-i} \in \{0,1\}^{i-1}} \frac{1}{c}L\left(\mathbf \xi_{-i}^TA_{-i}\xi_{-i}\right) L'\left(\mathbf{a}_i^T\left[\begin{array}{c} \mathbf \xi_{-i} \\ 1 \end{array}\right]\right)\left[\begin{array}{c} \xi_{-i} \\ 1 \end{array}\right]\left[\begin{array}{cc} \xi_{-i}^T & 1 \end{array}\right]. \]
